---
title: "p8105_hw6_yl4610"
output: github_document
author: "Yuxin Liu"
date: "2022-11-21"
---

```{r setup, message=FALSE}
library(tidyverse)
library(modelr)
library(skimr)
```

# Question 2
```{r, message=FALSE}
homicide_raw = 
  read_csv( "./data/homicide_data.csv") %>% 
    mutate (
    city_state = str_c(city, ", ", state),
    result = ifelse(disposition != "Closed by arrest", "unsolved", "solved")) %>% 
    filter(!(city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"))) %>% 
    filter(victim_race %in% c("White", "Black")) %>% 
    filter(!(victim_age %in% c("Unknown"))) %>% 
    mutate (victim_age = as.numeric(victim_age))

homicide_raw 
```
I used mutate to create a city_state variable and a binary variable indicating whether the homicide is solved. I used filter to omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO; Tulsa, AL. Also, I used filter to limit victim_race as White or Black and delete unknown age. Lastly, I used mutate to change victim_age to numeric format.

```{r}
Baltimore_reg = 
 homicide_raw %>% 
  filter(city_state == "Baltimore, MD") %>%
  mutate (y_var = ifelse(result == "solved",0,1)) %>% 
    glm(y_var ~ victim_age + victim_sex + victim_race, data =., family = 'binomial'(link='logit')) %>% 
    broom::tidy () %>% 
    mutate(odds_ratio = exp(estimate),
           lower_bound = exp(estimate - 1.96 * std.error),
           upper_bound = exp(estimate + 1.96 * std.error)) %>% 
    select(term, estimate, odds_ratio, lower_bound,upper_bound ) %>% 
    filter(term == "victim_sexMale") 

Baltimore_reg
```
For the city of Baltimore, MD, I used the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
homicide_all_cities = 
  homicide_raw %>% 
  mutate (y_var = ifelse(result == "solved",0,1)) %>%
  nest(data = -city_state) %>% 
  mutate(
    glm_all_cities = map(data, ~glm(y_var ~ victim_age + victim_sex + victim_race, data = ., family = 'binomial'(link='logit'))),
    final_results = map(glm_all_cities, broom::tidy)) %>% 
  unnest(final_results) %>% 
  mutate(
    odds_ratio = exp(estimate),
    lower_bound = exp(estimate - 1.96 * std.error),
    upper_bound = exp(estimate + 1.96 * std.error)) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, odds_ratio, lower_bound,upper_bound) 

homicide_all_cities
```
I run glm for each of the cities, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. I did this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest to create a dataframe with estimated ORs and CIs for each city.

```{r}
homicide_plot = 
  homicide_all_cities %>% 
    mutate(city_state = fct_reorder(city_state, odds_ratio)) %>% 
    ggplot(aes(x = city_state, y = odds_ratio, color = city_state)) + 
    geom_point() + 
    geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound)) + 
    theme(axis.text.x = element_text(angle=90, hjust = 1)) + 
    labs(x = "City States",
         y = "Estimated Odds Ratios",
         title = "estimated ORs and CIs for each city") +
    theme(legend.position = "none") 

homicide_plot
```

I created a plot that shows the estimated ORs and CIs for each city. Then I organized cities according to estimated OR.
This scatter plot shows that New York, NY has the highest estimated odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed, while Albuquerque, NM has the lowest estimated odds ratio.

# Question 3 
```{r, message = FALSE}
birthweight_raw = 
  read_csv("./data/birthweight.csv") %>% 
    mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace))
```

```{r}
skimr::skim(birthweight_raw) 
```
There is no missing data.
I Loaded and cleaned the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
model = lm(bwt ~ ., data = birthweight_raw) %>%
  broom::tidy() %>% 
  knitr::kable(digits = 4)

regression_model = 
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_raw) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 4)

regression_model
```
I proposed a regression model for birthweight. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

